Submission HW1

### 2022-08-31 hw1-1/submission.Rmd
added abhinav ques 2.1

@@

>>>>

### Example 2: Readmission classification in Healthcare analytics

An example of classification problem in Healthcare domain is the classification of whether a patient will get readmitted or not within 30 days of being discharged from a acute hospital setting. Having a good predictive model of the same can help us to curb the healthcare expenditure as the estimated average cost of readmission is more than \$10k.

**Objective Function (**$Y$): To classify whether a readmission will happen within 30 days of the Inpatient discharge for a given patient.\
**Predictor Variables (**$X_i$): Some of the key predictor variables given below:

-   ***Length of stay*** : The period for which a patient stays in the Inpatient setting is a key predictor of readmission. A detailed analysis of the same shows that readmission probability is high for both low length of stay (when a patient is discharged earlier than expected without proper treatment) and even when length of stay is larger than a given threshold (because of patient acquiring healthcare associated infections over a prolonged period of stay).

-   ***Discharge Disposition*** : The place where a patient is discharged also a good predictor of whether a person will get readmitted or not within 30 days .For some of the diagnosis categories , if a patient is discharged to home in place of a Post acute care setting , the readmission rate is higher.

-   ***ED Utilization*** : The number of emergency department(ED) visits of a patient within a rolling 1 year is a good predictor of the risk profile of the patient and in turn it is a good predictor of whether a readmission will happen or not.

-   ***\# of changes in medications/procedures*** : The number of medication changes is also a good variable for predicting readmission . Higher \# of medication changes during hospital stay is correlated with the occurence of a patient being readmitted.

@@

###
